Analysis of Odd one out experiment

### 2019-06-03 reports/odd_one_out/analysis_oddoneout.Rmd
add new plots

participants <- readxl::read_excel("data/oddoneout/oddoneout_participants.xlsx")
```

```{create plot dir}
plots_dir <- here::here("plots")

if(!dir.exists(plots_dir)) {
  dir.create(plots_dir)
}

@@

>>>>

participants <- readxl::read_excel(here("data","oddoneout","oddoneout_participants.xlsx"))
```

```{r create plot dir}
plots_dir <- here::here("plots", "oddoneout")

if(!dir.exists(plots_dir)) {
  dir.create(plots_dir, recursive = T)
}

@@

## Histogram

```{r}

this_cat <- df %>% filter(subject_id == 1, trial_id == 1) %>% pull(category)
this_center <- df %>% filter(subject_id == 1, trial_id == 1) %>% pull(selected_image)

df_onecat_distances <- fc7[fc7_names == this_center, str_starts(fc7_names, this_cat)] %>% enframe() %>% rename(distance = value)

qs <- compute_quintiles(df_onecat_distances$distance) 
df_onecat_distances <- df_onecat_distances %>% 
  mutate(quintile = case_when(
    distance<qs[2] ~ 1,
    distance >= qs[2] & distance < qs[3] ~ 2,
    distance >= qs[3] & distance < qs[4] ~ 3,
    distance >= qs[4] & distance < qs[5] ~ 4,
    TRUE ~ 5
  ) %>% as.factor())

df_segments <- tibble(x = qs[2:6], xend = x, y = 0, yend = 17)

p <- df_onecat_distances %>% 
  ggplot(aes(x = distance)) + 
  geom_histogram(bins = 30) + 
  theme(aspect.ratio = 1) +
  geom_segment(data = df_segments, aes(x=x,xend=xend,y=y,yend=yend)) +
  annotate(x = qs[3:5]-c(3,1,0), y = c(19,19,19), label = c("2.","3.","4."), geom = "label") +
  ggtitle(sprintf("Kategorie: %s",this_cat)) +
  xlab("Vzdálenost") +
  ylab("Počet")
p  
ggsave(file.path(plots_dir, "Fig_distance_histogram.eps"), p, width = 6, height = 6)  
```
